Manifold Destiny - or how to rig an election

### 2023-12-28 index.qmd
befrev
lastimupd
abc

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("dplyr","purrr","magrittr","data.table","tidyr"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
```

# Simulation
## R2 sim
```{webr-r}
dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
probw <- c(m=0.51,s=0.10)
probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
ztech <- c(0,1)	
app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
SimVoterdatabase(app_bal)
```

>>>>

### Install and load packages
```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("dplyr","purrr","magrittr","data.table","tidyr","plotly"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
```

### Simulation
```{webr-r}
dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
probw <- c(m=0.51,s=0.10)
probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
ztech <- c(0,1)	
app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
SimVoterdatabase(app_bal)
```
**Last time updated: `r as.Date(Sys.time())`**

### Simulation
```{webr-r}
library(plotly)
options(browser = 'brave') 
mtcars$am[which(mtcars$am == 0)] <- 'Automatic'
mtcars$am[which(mtcars$am == 1)] <- 'Manual'
mtcars$am <- as.factor(mtcars$am)

fig <- plot_ly(mtcars, x = ~wt, y = ~hp, z = ~qsec, color = ~am, colors = c('#BF382A', '#0C4B8E'))
fig <- fig %>% add_markers()
fig <- fig %>% layout(scene = list(xaxis = list(title = 'Weight'),
                     yaxis = list(title = 'Gross horsepower'),
                     zaxis = list(title = '1/4 mile time')))

fig
```
